EoS-insensitive relations after GW170817

### 2019-02-06 paper/bin-love-after-gw170817.tex
minor

In addition, Fig.~\ref{fig:rlove} displays the relationship between the NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
This relationship is computed directly from the C-Love relations discussed above as $R(\Lambda)=m/C(\Lambda)$ for observed mass $m=1.48\text{ M}_{\odot}$ from GW170817.
We also present the uncertainty on a NS radius measurement using the C-Love relations in the bottom panel of Fig.~\ref{fig:rlove}, defined as the absolute difference from the fits.
We observe a large suppression in the radius measurement accuracy from the unconstrained set of EoSs to the constrained set, tabulated in Tab.~\ref{tab:maxVar} as the maximal EoS measurement uncertainty.

@@

Figure~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both the constrained and unconstrained sets of EoSs.
%In this figure we show the absolute difference from the fit, rather than the fractional difference, so one can see which regions of $\Lambda_s$ display the largest actual difference.
\zc{need to decide if using fractional or actual here}
Observe how once again, the constrained set of EoSs show a considerable improvement upon both the unconstrained set of EoSs, as well as the results found in previous works~\cite{Yagi:binLove}.
Additionally, the unconstrained set of EoSs show similar, yet slightly larger EoS variation than was previously found in Ref.~\cite{Yagi:binLove} due to the random sampling taken into account in this analysis.
Once again, the maximum EoS variability (in terms of fractional difference from the fit for comparison purposes) is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio.

@@

{\ny{Super confused about Fig. 1...}}
\kc{me too}
{\zc{Yes, there is a \emph{lot} of info in this figure. The filled blue circles are the statistical uncertainties on $\lambda_0$ for GW170817 as if it had been detected on Detector A=(O2, aLIGO, A+, Voyager, ET, CE), where the x-axis corresponds to the SNR on that detector as if it found GW170817. The filled turquoise region is the combined statistical uncertainty on the detection of $N_A$ events on each detector A, computed using the bulleted process above (moved to the appendix). There is some height to this shaded region because I consider the the upper and lower error bars of the local BNS merger rate $\mathcal{R}$ - giving us a range of $N_A$'s to consider for each detector. We can talk more about this over Skype.}}

>>>>

In addition, Fig.~\ref{fig:rlove} displays the relationship between the NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
This relationship is computed directly from the C-Love relations discussed above as $R(\Lambda)=m/C(\Lambda)$ for observed mass $m=1.48\text{ M}_{\odot}$ from GW170817.
We also present the uncertainty on a NS radius measurement using the C-Love relations in the bottom panel of Fig.~\ref{fig:rlove}, defined as the absolute difference from the fits.
We observe a large suppression in the radius measurement accuracy from the unconstrained set of EoSs to the constrained set, tabulated in Tab.~\ref{tab:maxVar} as the maximal EoS measurement uncertainty.
{\ny{That's a good idea. But it is not immediately obvious that this will help. Kent and I have found that when you look at relations between dimensionless quantities, then the universality is typically stronger than when you use dimensionful quantities (incidentally, this is why the Doneva paper about rapidly-rotating I-Love-Q is wrong, as pointed out by Haris and George).}}

@@

Figure~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both the constrained and unconstrained sets of EoSs.
\zc{need to decide if using fractional or actual here}
Observe how once again, the constrained set of EoSs show a considerable improvement upon both the unconstrained set of EoSs, as well as the results found in previous works~\cite{Yagi:binLove}.
Additionally, the unconstrained set of EoSs show similar, yet slightly larger EoS variation than was previously found in Ref.~\cite{Yagi:binLove} due to the random sampling taken into account in this analysis.
Once again, the maximum EoS variability (in terms of fractional difference from the fit for comparison purposes) is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio.

@@

{\ny{Super confused about Fig. 1...}}
\kc{me too}
{\zc{Yes, there is a \emph{lot} of info in this figure. The filled blue circles are the statistical uncertainties on $\lambda_0$ for GW170817 as if it had been detected on Detector A=(O2, aLIGO, A+, Voyager, ET, CE), where the x-axis corresponds to the SNR on that detector as if it found GW170817. The filled turquoise region is the combined statistical uncertainty on the detection of $N_A$ events on each detector A, computed using the bulleted process above (moved to the appendix). There is some height to this shaded region because I consider the the upper and lower error bars of the local BNS merger rate $\mathcal{R}$ - giving us a range of $N_A$'s to consider for each detector. We can talk more about this over Skype.}} 
{\ny{I'm happier with this rewrite (makes more sense to me now).}}
